# Offense Segment

```{r, echo=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  error   = FALSE,
  message = FALSE
)
```

```{r,  results='hide'}
load("data/nibrs_offense_segment_segment_2019.rda")
offense <- nibrs_offense_segment_segment_2019
rm(nibrs_offense_segment_segment_2019)
gc()
```




## Important variables

### Crime category

```{r offenseCrimeCategories, fig.cap = "The number and percent of crimes reported from all agencies in 2019, by crime category."}

temp <- make_frequency_table(offense,
                             "ucr_offense_code",
                             c("Crime Category",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```

### Offense subtype

```{r offenseCrimeSubcategories, fig.cap = "The number and percent of crimes reported from all agencies in 2019, by crime category."}

temp <- make_frequency_table(offense,
                             "type_criminal_activity_1",
                             c("Crime Subcategory",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```

* Aggravated Assault
* Animal Cruelty
* Counterfeiting/Forgery
* Drug Equipment Violations
* Drug/Narcotic Violations
* Fondling (Incident Liberties/Child Molest)
* Gambling Equipment Violations
* Intimidation
* Kidnapping/Abduction
* Murder/Nonnegligent Manslaughter
* Negligent Manslaughter
* Pornography/Obscene Material
* Rape
* Robbery
* Sexual Assault With An Object
* Simple Assault
* Sodomy
* Stolen Property Offenses (Receiving, Selling, Etc.)
* Weapon Law Violations

```{r offenseCrimeSubcategoriesAnimalAbuse, fig.cap = "The number and percent of crimes reported from all agencies in 2019, by crime category."}

temp <- make_frequency_table(offense[offense$ucr_offense_code %in% "animal cruelty", ],
                             "type_criminal_activity_1",
                             c("Crime Subcategory",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```

### Drug, alcohol, or computer use

```{r}
offense %>%
  mutate(offender_suspected_of_using_1 = capitalize_words(offender_suspected_of_using_1)) %>%
crimeutils::make_barplots("offender_suspected_of_using_1", count = FALSE, ylab = "% of Offenses") +
  ggplot2::scale_y_continuous(labels = scales::percent)
```

```{r}
offense %>%
  filter(offender_suspected_of_using_1 != "not applicable") %>%
  mutate(offender_suspected_of_using_1 = capitalize_words(offender_suspected_of_using_1)) %>%
crimeutils::make_barplots("offender_suspected_of_using_1", count = FALSE, ylab = "% of Offenses") +
  ggplot2::scale_y_continuous(labels = scales::percent)
```

### Crime location

```{r offenseLocation, fig.cap = "The location of crimes for all offenses reported in 2019."}

temp <- make_frequency_table(offense,
                             "location_type",
                             c("Crime Location",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```

### Weapons

```{r offenseWeapon, fig.cap = "The bias motivation (i.e. if hate crime or not) for all offenses reported in 2019."}

temp <- make_frequency_table(offense,
                             "type_weapon_force_involved_1",
                             c("Weapon Used",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```

* Aggravated Assault
* Extortion/Blackmail
* Fondling (Incident Liberties/Child Molest)
* Human Trafficking - Commercial Sex Acts
* Human Trafficking - Involuntary Servitude
* Justifiable Homicide
* Kidnapping/Abduction
* Murder/Nonnegligent Manslaughter
* Negligent Manslaughter
* Rape
* Robbery
* Sexual Assault With An Object
* Simple Assault
* Sodomy
* Weapon Law Violations

### Automatic weapons

This variable only tells you if the weapon is automatic 

```{r}
temp <- 
  offense %>%
  filter(type_weapon_force_involved_1 %in% c("firearm (type not stated)",
                                             "handgun ",
                                             "other firearm",
                                             "rifle",
                                             "shotgun"))
temp$automatic_binary <- 0
temp$automatic_binary[temp$automatic_weapon_indicator_1 %in% "automatic weapon"] <- 1

temp <- 
  temp %>%
  group_by(type_weapon_force_involved_1) %>%
  summarize(automatic_weapon = mean(automatic_binary)) %>%
  mutate(type_weapon_force_involved_1 = capitalize_words(type_weapon_force_involved_1)) %>%
  arrange(desc(automatic_weapon))
temp$type_weapon_force_involved_1 <- factor(temp$type_weapon_force_involved_1, 
                                            levels = rev(temp$type_weapon_force_involved_1))


ggplot(temp, aes(x = type_weapon_force_involved_1, y = automatic_weapon)) +
  geom_col() +
  coord_flip() + 
  ggplot2::scale_y_continuous(labels = scales::percent) + 
  xlab("Weapon") +
  ylab("% Automatic Weapon") + 
  theme_crim()

```

### Hate crime indicator (bias motivation)

```{r offenseBiasMotivation, fig.cap = "The bias motivation (i.e. if hate crime or not) for all offenses reported in 2019."}

temp <- make_frequency_table(offense,
                             "bias_motivation",
                             c("Bias Motivation",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```


```{r offenseBiasMotivationBiases, fig.cap = "The bias motivation (i.e. if hate crime or not) for all offenses reported in 2019 that were classifed as hate crimes."}

temp <- make_frequency_table(offense[!offense$bias_motivation %in% c("no bias motivation",
                                                                     "unknown bias motivation"),],
                             "bias_motivation",
                             c("Bias Motivation",
                               "# of Offenses",
                               "% of Offenses"))
datatable(temp, options = list(pageLength = 100)) %>%
  formatPercentage('% of Offenses', 2) %>%
  formatRound('# of Offenses', digits = 0)
```